\textbf{On the (non-)exhaustivity of naturally occurring \whqs}

### 2022-11-03 analysis/exploratory/all_nocontext/rscripts/graphs.Rmd
better graphs for exps 1a and 1b

########################################################################
# Read the data into R.
```{r}
rq = read.csv("../../../03_experiment/data/normed.csv")
eq = read.csv("../../../04_experiment/data/normed.csv")
rq = rq[,c("workerid","tgrep_id","ModalPresent","Modal","QuestionType","Question","Sentence","paraphrase","normed_rating","Finite","Wh")]
eq = eq[,c("workerid","tgrep_id","ModalPresent","Modal","QuestionType","Question","Sentence","paraphrase","normed_rating","Finite","Wh","VerbLemma")]

@@

ggplot(data = agr, aes(x = mean_rating, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  # facet_grid(~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/denisty_mean_ratings.pdf",width=5,height=3)

@@

ggplot(data = agr, aes(x = mean_rating, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  facet_grid(Wh~ModalPresent) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/denisty_mean_ratings_factors.pdf",width=5,height=5)

@@

## Graphs of Proportion
```{r}
# OVERALL
agr = normed %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

dodge = position_dodge(.9)
ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  ylim(0,.6) +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/overall_critical.pdf",width=2,height=2)
```

########################################################################
# OVERALL QUESTION TYPE
```{r}
sai = normed %>%
  filter((QuestionType == "embeddedSAI")) %>% #  & (Wh == "why")
  group_by(tgrep_id,Sentence,VerbLemma,Question,paraphrase) %>%
  summarize(mean_rating = mean(rating), sd = sd(rating)) %>%
  filter(mean_rating > .5) %>%
  View()

agr = normed %>%
  group_by(QuestionType,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=QuestionType, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  # facet_grid(EmbeddedSQ~Wh) +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  # guides(alpha=guide_legend(title="Embedded SAI")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/overall_QT.pdf",width=3,height=3)
```
########################################################################
# OVERALL MOD x WH
```{r}
agr = normed %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

# ggsave("../graphs/modxwh_critical.pdf",width=3,height=4)

```
########################################################################
# OVERALL MOD x WH x QUESTIONTYPE
```{r}
agr = d %>%
  group_by(QuestionType,Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=ModalPresent, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_grid(QuestionType~Wh) +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  # ggtitle("overall ratings for SAI in test qs") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Modal present")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/modxwh_QT.pdf",width=8,height=6)
```
########################################################################
# LOOKING AT verbs
########################################################################
```{r, include=FALSE}
verb_count = eq %>%
  group_by(VerbLemma) %>%
  summarize(count = n())
View(verb_count)

agr = eq %>%
  filter(VerbLemma == "know") %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

# ggsave("../graphs/modwh_know.pdf",width=3,height=4)
```

@@

```{r, include=FALSE}
agr = eq %>%
  # Most frequent
  filter(VerbLemma %in% c("know","see","wonder","understand","be","tell","figure","say","think","sure","learn","remember")) %>%
  group_by(paraphrase,VerbLemma,ModalPresent) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

# ggsave("../graphs/matrixverbs_frequent.pdf",width=6,height=5)
```

@@

agr = d %>%   
  filter(ModalPresent %in% c("yes")) %>%
  group_by(Modal,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh)

ggplot(agr, aes(x=paraphrase,y=mean_rating,fill=paraphrase)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Modal,ncol=5) +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/modals.pdf",,width=5,height=3)
```

>>>>

########################################################################
# Read the data into R.
```{r}
rq = read.csv("../../../03_experiment/data/normed.csv")
eq = read.csv("../../../04_experiment/data/normed.csv")

# names(rq)

rq = rq[,c("workerid","tgrep_id","ModalPresent","Modal","QuestionType","Sentence","paraphrase","normed_rating","Finite","Wh")]
eq = eq[,c("workerid","tgrep_id","ModalPresent","Modal","QuestionType","Sentence","paraphrase","normed_rating","Finite","Wh","VerbLemma")]

@@

ggplot(data = agr, aes(x = mean_rating, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  # facet_grid(~paraphrase) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/denisty_mean_ratings_context.pdf",width=5,height=3)

@@

ggplot(data = agr, aes(x = mean_rating, fill=paraphrase, color=paraphrase)) +
  geom_density(alpha = .4) +
  facet_grid(Wh~ModalPresent) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/denisty_mean_ratings_factors_context.pdf",width=5,height=5)

@@

## Graphs of Proportion
```{r}
# OVERALL
agr = d %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

dodge = position_dodge(.9)
ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position=dodge,stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=dodge, show.legend = FALSE) +
  # ggtitle("Mean rating for 'a' vs. 'every'") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  ylim(0,.6) +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/overall_context.pdf",width=2,height=2)
```

########################################################################
# MOD x WH
```{r}
agr = d %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

ggsave("../graphs/modxwh_context.pdf",width=3,height=4)

########################################################################
# OVERALL QUESTION TYPE
```{r}
# sai = d %>%
#   filter((QuestionType == "embeddedSAI")) %>% #  & (Wh == "why")
#   group_by(tgrep_id,Sentence,VerbLemma,Question,paraphrase) %>%
#   summarize(mean_rating = mean(normed_rating), sd = sd(normed_rating)) %>%
#   filter(mean_rating > .5) %>%
#   View()

agr = d %>%
  group_by(QuestionType,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=QuestionType, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  # facet_grid(EmbeddedSQ~Wh) +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  guides(fill=FALSE) +
  # guides(alpha=guide_legend(title="Embedded SAI")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/overall_context_QT.pdf",width=3,height=3)
```

########################################################################
# MOD x WH x QUESTIONTYPE
```{r}
agr = d %>%
  group_by(QuestionType,Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

ggplot(agr,aes(x=paraphrase, y=mean_rating, alpha=ModalPresent, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position=position_dodge(0.9)) +
  facet_grid(QuestionType~Wh) +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  # ggtitle("overall ratings for SAI in test qs") +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="Modal present")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/modxwh_context_QT.pdf",width=8,height=6)
```
########################################################################
# LOOKING AT verbs
########################################################################
```{r, include=FALSE}
verb_count = eq %>%
  group_by(VerbLemma) %>%
  summarize(count = n())
# View(verb_count)

agr = eq %>%
  filter(VerbLemma == "know") %>%
  group_by(Wh,ModalPresent,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

# ggsave("../graphs/modwh_know-context.pdf",width=3,height=4)
```

@@

```{r, include=FALSE}
agr = eq %>%
  # Most frequent
  filter(VerbLemma %in% c("know","see","wonder","understand","be","tell","figure","say","think","sure","learn","remember")) %>%
  group_by(paraphrase,VerbLemma,ModalPresent) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

@@

# ggsave("../graphs/matrixverbs_frequent_context.pdf",width=6,height=5)
```

@@

agr = d %>%   
  filter(ModalPresent %in% c("yes")) %>%
  group_by(Modal,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh)

ggplot(agr, aes(x=paraphrase,y=mean_rating,fill=paraphrase)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Modal,ncol=5) +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/modals_context.pdf",,width=5,height=3)
```

### 2022-11-03 analysis/exploratory/context_versus_nocontext/rscripts/analysis.Rmd
better graphs for exps 1a and 1b

```{r set the reference levels for wh}
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))
```

>>>>

```{r set the reference levels for wh}
# Set the reference levels
contrasts(d.ms.ma$Wh) = cbind("how.vs.when"=c(0,1,0,0,0,0),"what.vs.when"=c(1,0,0,0,0,0),
                "where.vs.when"=c(0,0,0,1,0,0),"who.vs.when"=c(0,0,0,0,1,0),
                "why.vs.when"=c(0,0,0,0,0,1))

d.ms.ma$paraphrase.dc <- as.factor(d.ms.ma$paraphrase.dc)
contrasts(d.ms.ma$paraphrase.dc)
contrasts(d.ms.ma$Task)

View(d.ms.ma)
contrasts(d.ms.ma$Wh)
```

### 2022-11-03 papers/article/main.tex
better graphs for exps 1a and 1b

Analysis were conducted to assess the effect of Task (Context, NoContext) in addition to modality and \whw on question interpretation. Given the potential 4-way interaction by including Task as a predictor, we broke the data set up by Paraphrase and conducted three sub-model analysis.

@@

Table \ref{sub-model_Task} presents regression results assessing the effect of Context (Task) on \emph{a}- and \emph{every}- paraphrase ratings.
{}
% TASK COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for overall Task x Paraphrase model in metanalaysis comparing Context and NoContext tasks. Both predictors are dummy-coded and centered (0 is no Context and \emph{every}-paraphrase, 1 for Modal is present and \emph{a}-paraphrase.} 
\label{sub-model_Task} 
% \vskip .12in
\begin{tabular}{lllll} 
\toprule
{} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
Intercept & .22 & .003 & 80.66 & $<$.0001\\
Paraphrase & .01 & .006 & 2.26 & $<$.03\\
% \rowcolor{Gainsboro!100}
Task & -.01 & .003 & -4.75 & $<$.0001\\
% \rowcolor{Gainsboro!100}
Paraphrase:Task & .07 & .008 & 8.7 & $<$.0001\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

@@

@@

% TASK-A SUBMODEL COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for Task x ModalPresent \emph{wh}-word submodels for the data subsetted to \emph{a}-paraphrases. Both predictors are dummy-coded and centered (0 is no Context, 1 for Modal is present.} 
\label{sub-models_Task-a} 
% \vskip .12in
\begin{tabular}{l|lllll} 
\toprule
Wh-Word & {} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
WHAT & Intercept & .21 & .007 & 31.53 & $<$.0001\\
{} & ModalPresent & .1 & .01 & 11.15 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .3 & .007 & 4.37 & $<$.0002\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .01 & -2.86 & $<$.005\\
\bottomrule
\toprule
% HOW & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
HOW & Intercept & .25 & .006 & 42.91 & $<$.0001\\
{} & ModalPresent & .08 & .01 & 6.87 & $<$ .0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .02 & .01 & 2.31 & $<$.05\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .001 & .01 & .07 & .94\\
% \bottomrule
\toprule
% WHERE & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHERE & Intercept & .22 & .02 & 14.7 & $<$.0001\\
{} & ModalPresent & .1 & .03 & 3.51 & $<$.0006\\
% \rowcolor{Gainsboro!100}
{} & Task & .01 & .02 & .8 & .44\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.02 & .03 & -.75 & .46\\
\bottomrule
\toprule
% {} & WHY & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHY & Intercept & .22 & .007 & 32.84 & $<$.0001\\
{} & ModalPresent & .09 & .02 & 5.82 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .02 & .01 & 1.27 & .24\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.02 & .02 & -.67 & .5\\
\bottomrule
\toprule
% WHO & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHO & Intercept & .26 & .03 & 9.12 & $<$.0001\\
{} & ModalPresent & .12 & .04 & 2.92 & $<$.005\\
% \rowcolor{Gainsboro!100}
{} & Task & .04 & .01 & 2.87 & $<$.04\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .04 & -.81 & .42\\
\bottomrule
\toprule
% WHEN & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHEN & Intercept & .27 & .03 & 9.25 & $<$.0001\\
{} & ModalPresent & .22 & .07 & 3.44 & $<$.002\\
% \rowcolor{Gainsboro!100}
{} & Paraphrase & -.01 & .03 & -.31 & .77\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Paraphrase & -.01 & .06 & -.24 & .81\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

% TASK-EVERY SUBMODEL COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for Task x ModalPresent \emph{wh}-word submodels for the data subsetted to \emph{every}-paraphrases. Both predictors are dummy-coded and centered (0 is no Context, 1 for Modal is present.} 
\label{sub-models_Task-every} 
% \vskip .12in
\begin{tabular}{l|lllll} 
\toprule
Wh-Word & {} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
WHAT & Intercept & .28 & .02 & 16.09 & $<$.0001\\
{} & ModalPresent & .05 & .02 & 3.05 & $<$.003\\
% \rowcolor{Gainsboro!100}
{} & Task & -.08 & .01 & -6.26 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .003 & .01 & .22 & .82\\
\bottomrule
\toprule
% HOW & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
HOW & Intercept & .17 & .01 & 14.83 & $<$.0001\\
{} & ModalPresent & -.01 & .01 & -.84 & .4\\
% \rowcolor{Gainsboro!100}
{} & Task & -.04 & .01 & -4.02 & $<$.0007\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.002 & .01 & -.19 & .85\\
% \bottomrule
\toprule
% WHERE & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHERE & Intercept & .19 & .02 & 8.01 & $<$.0001\\
{} & ModalPresent & -.04 & .04 & -.97 & .34\\
% \rowcolor{Gainsboro!100}
{} & Task & -.04 & .01 & -.422 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .03 & .03 & 1.03 & .3\\
\bottomrule
\toprule
% {} & WHY & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHY & Intercept & .15 & .01 & 17.2 & $<$.0001\\
{} & ModalPresent & -.001 & .02 & -.06 & .95\\
% \rowcolor{Gainsboro!100}
{} & Task & -.03 & .01 & -2.95 & $<$.005\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.01 & .02 & -.62 & .54\\
\bottomrule
\toprule
% WHO & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHO & Intercept & .23 & .02 & 10.35 & $<$.0001\\
{} & ModalPresent & .004 & .07 & .07 & .95\\
% \rowcolor{Gainsboro!100}
{} & Task & -.09 & .02 & -4.2 & $<$.002\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .05 & -.49 & .62\\
\bottomrule
\toprule
% WHEN & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHEN & Intercept & .16 & .04 & 4.31 & $<$.004\\
{} & ModalPresent & .02 & .06 & .31 & .76\\
% \rowcolor{Gainsboro!100}
{} & Paraphrase & -.02 & .02 & -1.01 & .28\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Paraphrase & .03 & .04 & .71 & .48\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

>>>>

Analysis were conducted to assess the effect of Task (Context, NoContext) in addition to modality and \whw on question interpretation. Given the potential 4-way interaction by including Task as a predictor, we first broke the data set up by Paraphrase and then conducted sub-model analysis by \emph{wh}-phrase as previously done for the earlier experiments.

@@

Table \ref{sub-model_Task} presents regression results assessing the effect of Context (Task) on \emph{a}- and \emph{every}- paraphrase ratings. We find first that there is a significant initial bias for \emph{a}- over \emph{every}-paraphrases, indicated by the positive oefficient for Paraphrase, and

First that there is a significant initial bias for \emph{a}-paraphrases
{}
% TASK COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for overall Task x Paraphrase model in metanalaysis comparing Context and NoContext tasks. Both predictors are dummy-coded and centered (0 is the Context Task and \emph{every}-paraphrase, 1 for Modal is present and \emph{a}-paraphrase.} 
\label{sub-model_Task} 
% \vskip .12in
\begin{tabular}{lllll} 
\toprule
{} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
Intercept & .22 & .003 & 80.66 & $<$.0001\\
Paraphrase & .01 & .006 & 2.26 & $<$.03\\
% \rowcolor{Gainsboro!100}
Task & -.01 & .003 & -4.75 & $<$.0001\\
% \rowcolor{Gainsboro!100}
Paraphrase:Task & .07 & .008 & 8.7 & $<$.0001\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

@@

Table \ref{sub-models_Task-a} presents the regression results for the effect of Task and ModalPresent on \emph{a}-paraphrases, split up into submodels for each \emph{wh}-phrase to facilitate model interpretation.

@@

Table \ref{sub-models_Task-every} presents the regression results for the effect of Task and ModalPresent on \emph{every}-paraphrases, split up into submodels for each \emph{wh}-phrase to facilitate model interpretation.

% TASK-A SUBMODEL COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for Task x ModalPresent \emph{wh}-word submodels for the data subsetted to \emph{a}-paraphrases. Both predictors are dummy-coded and centered (0 is the Context Task, 1 for Modal is present.} 
\label{sub-models_Task-a} 
% \vskip .12in
\begin{tabular}{l|lllll} 
\toprule
Wh-Word & {} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
WHAT & Intercept & .21 & .007 & 31.53 & $<$.0001\\
{} & ModalPresent & .1 & .01 & 11.15 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .3 & .007 & 4.37 & $<$.0002\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .01 & -2.86 & $<$.005\\
\bottomrule
\toprule
% HOW & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
HOW & Intercept & .25 & .006 & 42.91 & $<$.0001\\
{} & ModalPresent & .08 & .01 & 6.87 & $<$ .0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .02 & .01 & 2.31 & $<$.05\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .001 & .01 & .07 & .94\\
% \bottomrule
\toprule
% WHERE & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHERE & Intercept & .22 & .02 & 14.7 & $<$.0001\\
{} & ModalPresent & .1 & .03 & 3.51 & $<$.0006\\
% \rowcolor{Gainsboro!100}
{} & Task & .01 & .02 & .8 & .44\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.02 & .03 & -.75 & .46\\
\bottomrule
\toprule
% {} & WHY & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHY & Intercept & .22 & .007 & 32.84 & $<$.0001\\
{} & ModalPresent & .09 & .02 & 5.82 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & Task & .02 & .01 & 1.27 & .24\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.02 & .02 & -.67 & .5\\
\bottomrule
\toprule
% WHO & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHO & Intercept & .26 & .03 & 9.12 & $<$.0001\\
{} & ModalPresent & .12 & .04 & 2.92 & $<$.005\\
% \rowcolor{Gainsboro!100}
{} & Task & .04 & .01 & 2.87 & $<$.04\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .04 & -.81 & .42\\
\bottomrule
\toprule
% WHEN & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHEN & Intercept & .27 & .03 & 9.25 & $<$.0001\\
{} & ModalPresent & .22 & .07 & 3.44 & $<$.002\\
% \rowcolor{Gainsboro!100}
{} & Paraphrase & -.01 & .03 & -.31 & .77\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Paraphrase & -.01 & .06 & -.24 & .81\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}

% TASK-EVERY SUBMODEL COEFFICIENT TABLE
\begin{table}
\begin{center} 
\caption{Coefficient table (predicted $\beta$ coefficient, standard error $SE$, $t$ value, and $p$ value) for Task x ModalPresent \emph{wh}-word submodels for the data subsetted to \emph{every}-paraphrases. Both predictors are dummy-coded and centered (0 is the Context Task, 1 for Modal is present.} 
\label{sub-models_Task-every} 
% \vskip .12in
\begin{tabular}{l|lllll} 
\toprule
Wh-Word & {} & $\beta$ & $SE$ & $t$ & $p$\\
\midrule
WHAT & Intercept & .28 & .02 & 16.09 & $<$.0001\\
{} & ModalPresent & .05 & .02 & 3.05 & $<$.003\\
% \rowcolor{Gainsboro!100}
{} & Task & -.08 & .01 & -6.26 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .003 & .01 & .22 & .82\\
\bottomrule
\toprule
% HOW & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
HOW & Intercept & .17 & .01 & 14.83 & $<$.0001\\
{} & ModalPresent & -.01 & .01 & -.84 & .4\\
% \rowcolor{Gainsboro!100}
{} & Task & -.04 & .01 & -4.02 & $<$.0007\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.002 & .01 & -.19 & .85\\
% \bottomrule
\toprule
% WHERE & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHERE & Intercept & .19 & .02 & 8.01 & $<$.0001\\
{} & ModalPresent & -.04 & .04 & -.97 & .34\\
% \rowcolor{Gainsboro!100}
{} & Task & -.04 & .01 & -.422 & $<$.0001\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & .03 & .03 & 1.03 & .3\\
\bottomrule
\toprule
% {} & WHY & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHY & Intercept & .15 & .01 & 17.2 & $<$.0001\\
{} & ModalPresent & -.001 & .02 & -.06 & .95\\
% \rowcolor{Gainsboro!100}
{} & Task & -.03 & .01 & -2.95 & $<$.005\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.01 & .02 & -.62 & .54\\
\bottomrule
\toprule
% WHO & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHO & Intercept & .23 & .02 & 10.35 & $<$.0001\\
{} & ModalPresent & .004 & .07 & .07 & .95\\
% \rowcolor{Gainsboro!100}
{} & Task & -.09 & .02 & -4.2 & $<$.002\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Task & -.03 & .05 & -.49 & .62\\
\bottomrule
\toprule
% WHEN & $\beta$ & $SE$ & $t$ & $p$\\
% \midrule
WHEN & Intercept & .16 & .04 & 4.31 & $<$.004\\
{} & ModalPresent & .02 & .06 & .31 & .76\\
% \rowcolor{Gainsboro!100}
{} & Paraphrase & -.02 & .02 & -1.01 & .28\\
% \rowcolor{Gainsboro!100}
{} & ModalPresent:Paraphrase & .03 & .04 & .71 & .48\\
\bottomrule
\end{tabular} 
\end{center} 
\end{table}
